Interfering with Noninterference \iftext\thanks{\bcp{Identify applicable funding agencies here (DARPA and NSF and...?)}}\fi

### 2020-02-04 main.tex
Fix problem with line breaks inside comments

\bcp{I'm nervous that these papers may be viewed as subsuming most of
  ours---in particular, their security property is formulated as a logical
  relation, i.e. a relational property!  We really need to dig into the
  details (which are unfortunately rather technical).}
\end{itemize}

>>>>

\bcp{I'm nervous that these papers may be viewed as subsuming most of
  ours---in particular, their security property is formulated as a logical
  relation, i.e. a relational property!  We really need to dig into the
  details (which are unfortunately rather technical).}

\rb{
  Some notes on StkTokens.
}
\rb{
  A calling convention based on linear capabilities to enforce WBCF and LCE. The
  program is divided into mutually distrustful components. Instead of using
  separate stacks for each component and a shared control stack, it uses a
  single shared stack. For this, it needs to pass stack and return capabilities
  to possibly untrusted components temporarily, revoking them later. Together
  with a small number of security checks, these measures suffice to guarantee
  WBCF and LCE. StkTokens employs linear capabilities to obtain this kind of
  result while limiting the amount of overhead needed to secure the transitions
  between boundary crossings, modeled by a standard notion of components,
  linking, disjoint interfaces, etc.
}
\rb{
  The capability machine that is modeled has two final configurations: halted
  (for successful termination) and failed. It is a mostly standard capability
  machine, modified by the additional requirements of linear capabilities
  (moves, stores and loads, seals, splitting and splicing of ranges of
  capability).
}
\rb{
  The formalization relies on the definition of a second operational semantics
  for the target language, where WBCF and LCE are natively enforced, and a proof
  of FA between that and the original operational semantics of the target. This
  semantics executes in lockstep with the original target semantics; in
  addition, it gives a special interpretation to the sequence of call
  instructions on top of the regular step relation. It assumes that all
  components meet some syntactic well-formedness requirements, and requires
  trusted components to perform a number of simple checks in addition to
  employing the calling convention proper (check of stack base address on call,
  appropriate use and protection of return and closure seals), as well as some
  conditions on initial system configurations. The formalization has a number
  of advantages over previous work, notably the establishment of some temporal
  safety guarantees.
}
\rb{
  The core of the proof of FA is the definition of when two components are
  related. This is modeled by a step-indexed Kripke logical with recursive
  worlds, which each collect assumptions about the system. Worlds are divided
  into sub-worlds for heap, call stack and free stack, each mapping region names
  to regions, which can be either spatial (all three) or shared (heap only,
  encapsulating a system invariant, including an invariant on seals). Spatial
  regions differ from shared regions in their linearity and (optionally)
  ownership. ``Regular'' spatial regions can become owned or revoked without
  while preserving the relation between memories in the two semantics. The proof
  uses (shared) code regions, regions for heap and stack memory, and regions to
  track immutable, inactive parts of the stack. With those Kripke worlds, the LR
  defines relatedness of various entities. There are two value relations for
  trusted and untrusted values (a subset of trusted values which are safe to
  pass to an adversary, including stack pointers and their linear capabilities,
  and sealed values, all under certain conditions on the ownership of the
  various parts of the stack). The top-level FA proof is straightforward.
}
\rb{
  The extended operational semantics has support for tail calls. Because data
  memory does not contain any seals or ways to get to those, it can always be
  shared safely.
}
\rb{
  Like in our scheme, instructions must be marked as executable and a check on
  the PC made at each step. Stack pointers are now linear stack capabilities
  (and there should only be stack pointers for the stack memory). Return
  pointers are pairs of sealed return capabilities, encapsulating the callers
  data and return code; the callee can only jump to these. A caller will split
  its own stack capability into two: one for its local stack frame (which will
  be sealed as the data component of the return capability pair) and one for the
  unused stack, which will be passed to the callee. This second capability is
  also used as a token to prove that the callee is allowed to return to the
  caller by adjacency with the sealed data capability (for this trick to work,
  stack frames must be non-empty). Another requirement is that each call point
  needs to be associated with a unique seal for returns, which should never be
  leaked to an adversary.
}
\rb{
  In their ESOP 2018 paper, the same authors present a similar scheme that uses
  local capabilities employing similar techniques. Their capability machine is
  mostly standard. Operations other than those working on capabilities are
  mostly standard, with small extensions to account for the presence
  capabilities. Notably, jmp needs to account for enter capabilities, which can
  only be used to jump to a location and then become read-execute; they
  represent an opaque packing of some code together with local state. The store
  operation is also complicated, this time by the presence of local
  capabilities, which can only be stored in registers (and write-local memory)
  and may be temporarily handed over to an adversary, say for the duration of a
  call.
}
\rb{
  The work presents a concrete calling convention that relies on a single shared
  stack and has moderate overhead with stack and return pointers passed through
  registers as local capabilities. The scheme imposes some standard conditions
  on initial state and memory allocation primitives, and safety measures a
  component needs to perform to protect itself against an adversary. The most
  demanding requirement is that not only non-return value registers and used
  stack, but also the unused part of the stack (which may contain local
  capabilities) needs to be cleared when returning to the adversary. Simple
  measures are applied on calls and returns to and from an adversary, and on
  calls from an adversary.
}
\rb{
  The logical relation that is presented is not specific to the particular
  calling convention. It uses a variant of the public-private separation of
  worlds to model the particular properties of local capabilities. In
  particular, worlds have permanent, temporary and revoked regions, with
  non-revoked regions comprising a state transition system with both public and
  private transitions. Local and global capabilities can depend on protocols
  from permanent regions, and local capabilities can also depend on protocols
  from temporary regions (which may be revoked in the future, and may not
  outlive those regions). A pair of future world relations describe the changes
  of memory over time. In the public FW relation, temporary and permanent
  regions can evolve according to the public part of their transition system,
  and revoked regions can be reinstated as temporary. In the private FW
  relation, temporary and revoked regions can be replaced by arbitrary regions,
  and permanent regions can evolve according to the private part of their
  transition system. The relation defines an observation relation for safe
  configurations (i.e., the memory of a halting configuration is satisfied by
  some private FW). The relation on values covers conditions for the safe use of
  write and write-local capabilities, and similarly for enter capabilities.
}
\rb{
  All this is used to prove WBCF and LCE for concrete example programs.
}
